\documentclass{article}
\usepackage{tocloft}
\include{common_symbols_and_format}
\renewcommand{\cfttoctitlefont}{\Large\bfseries}

\begin{document}
\logo
\rulename{Aroon} %Argument is name of rule
\tblofcontents

\ruledescription{The Aroon indicator is a technical indicator that is used to identify trend changes in the price of an asset, as well as the strength of that trend. In essence, the indicator measures the time between highs and the time between lows over a time period. The idea is that strong up trends will regularly see new highs, and strong downtrends will regularly see new lows. The indicator signals when this is happening, and when it isn't.
The indicator consists of the \textbf{"Aroon up"} line, which measures the strength of the uptrend, and the \textbf{"Aroon down"} line, which measures the strength of the downtrend.}

\howtotrade
{The strategy is to identify trend shifts or reversals.
Bullish Reversal - when Aroon up crossover above the Aroon down.
Bearish Reversal - when Aroon up crossover below the Aroon down.
}

\ruleparameters %You can include however many arguments (in groups of 4) as you want!
{High Periods}{25}{Periods Since \textit{\textbf{n}} period High}{$P_h$}
{Low Periods}{25}{Periods Since \textit{\textbf{n}} period Low}{$P_l$}
\stoptable %must be included or Tex engine runs infinitely


\section{Equation}
Below are the equations which govern how this specific trading rule calculates a trading position.

\begin{equation}
A_u = \frac{25 - P_h}{25} \times 100
\end{equation}

\begin{equation}
A_d = \frac{25 - P_l}{25} \times 100
\end{equation}


with:

$A_u$: is the AROON Up.

$A_d$: is the AROON Down.

$P_h$: Periods Since 25 period High.

$P_u$: Periods Since 25 period Low.


\keyterms
\furtherlinks %The footer
\end{document}