\documentclass{article}
\usepackage{tocloft}
\include{common_symbols_and_format}
\renewcommand{\cfttoctitlefont}{\Large\bfseries}
\begin{document}
\logo
\rulename{Differential of Moving Averages} %Argument is name of rule
\tblofcontents
\ruledescription{
This trading rules is a linear combination of four moving averages: short price average, long price average, short research average, long research average. The parameters accepted are the length of each average and coefficients for each average's weighting contribution. The total sum is divided by the current price to calculate a (dimensionless) position size.\\ 

\noindent Due to the linear summation this rule is only valid for research series of the same dimensionality as the price series (e.g. a research series representing a price target).\\

\noindent The last available value is included. As such if the short average is ``1" and the long average is ``1" then the short average is today's price and the long average is the average of today and yesterday's prices.\\

\noindent If a non-integer length is supplied then the average weights the contribution earliest date by the non-integer residual, such that average(6.75) is equivalent to (6 * average(6) + 0.75 * value(7)) / 6.75. This is prevent discontinuities as the lengths are increased.\\}

\ruleparameters
{Short price average length}{2.0}{Number of days in the short price average.}{$\averagelengthshort^{\price}$}
{Long price average length}{3.0}{Number of additional days in the longer price average (added to the number in the short price average).}{$\averagelengthlong^{\price}$}
{Short research average length}{2.0}{Number of days in the short research average.}{$\averagelengthshort^{\research}$}
{Long research average length}{3.0}{Number of additional days in the longer research average (added to the number in the short price average).}{$\averagelengthlong^{\research}$}
{Amplitude of short price average}{1.0}{Weighting coefficient for the short term average of price.}{$\amplitudecoefficientone^{\price}$}
{Amplitude of long price average}{1.0}{Weighting coefficient for the long term average of price.}{$\amplitudecoefficienttwo^{\price}$}
{Amplitude of short research average}{1.0}{Weighting coefficient for the short term average of research.}{$\amplitudecoefficientone^{\research}$}
{Amplitude of long research average}{1.0}{Weighting coefficient for the long term average of research.}{$\amplitudecoefficienttwo^{\research}$}
\stoptable

\section{Equation}

\begin{equation}
\bigcontribution(\currenttime, \averagelength, \amplitudecoefficient, \genericfunction) = \amplitudecoefficient \frac{(\averagelength - floor(\averagelength)) \genericfunction(\currenttime - ceil(\averagelength)) +  \sum_{\dummyiterator=0}^{\averagelength-1} \genericfunction(\currenttime - \dummyiterator))}{\averagelength}
\end{equation}

\begin{equation}
\position(\currenttime) = \frac{\bigcontribution(\currenttime, \averagelengthshort^{\price}, \amplitudecoefficientone^{\price}, \price)+\bigcontribution(\currenttime, (\averagelengthshort^{\price} + \averagelengthlong^{\price}), \amplitudecoefficienttwo^{\price},\price)+\bigcontribution(\currenttime, \averagelengthshort^{\research}, \amplitudecoefficientone^{\research}, \research)+\bigcontribution(\currenttime, (\averagelengthshort^{\research} + \averagelengthlong^{\research}), \amplitudecoefficienttwo^{\research}, \research)}{\price(\currenttime)}
\end{equation}\\


\noindent where $\position_\currenttime$ is the portfolio allocation at time $\currenttime$, $\price = \price(\currenttime)$ is the value of the price series and $\research = \research(\currenttime)$ is the value of the research series.

\hspace{200mm}
\hspace{200mm}

\keyterms
\furtherlinks

\end{document}
