\documentclass{article}
\usepackage{tocloft}
\include{common_symbols_and_format}
\renewcommand{\cfttoctitlefont}{\Large\bfseries}
\begin{document}
\logo
\rulename{Exponential Trading Rule - Two factor}

\tblofcontents

\ruledescription{These representations have the position dependent on an exponentially weighted average of the prior values of research and price. The look back length, $\lookbacklength$, determines how far back the rule looks. The decay rates, $\decaycoefficientone$ and $\decaycoefficienttwo$, and amplitudes, $\amplitudecoefficientone$ and $\amplitudecoefficienttwo$, coefficients determine the contribution from each exponential. The expression is normalised to be dimensionless by division by the weighting factors and current price.}

\ruleparameters
{Window size}{10}{This is the number of time steps over which exponential contributions are sourced.}{$\lookbacklength$}
{$1^{st}$ Exponential decay rate for price}{0.0}{This is the $1^{st}$ decay factor that reduces older contributions from the price series.}{$\decaycoefficientone^{\price}$}
{$1^{st}$ Exponential decay rate for research}{0.0}{This is the $1^{st}$ decay factor that reduces older contributions from the research series.}{$\decaycoefficientone^{\research}$}
{Amplitude of price $1^{st}$ contribution}{-0.1}{This factor scales the $1^{st}$ contribution from past values of price.}{$\amplitudecoefficientone^{\price}$}
{Amplitude of research $1^{st}$ contribution}{0.1}{This factor scales the $1^{st}$ contribution from past values of research.}{$\amplitudecoefficientone^{\research}$}
{$2^{nd}$ Exponential decay rate for price}{0.0}{This is the $2^{nd}$ decay factor that reduces older contributions from the price series.}{$\decaycoefficienttwo^{\price}$}
{$2^{nd}$ Exponential decay rate for research}{0.0}{This is the $2^{nd}$ decay factor that reduces older contributions from the research series.}{$\decaycoefficienttwo^{\research}$}
{Amplitude of $2^{nd}$ price contribution}{-0.1}{This factor scales the $2^{nd}$ contribution from past values of price.}{$\amplitudecoefficienttwo^{\price}$}
{Amplitude of $2^{nd}$ research contribution}{0.1}{This factor scales the $2^{nd}$ contribution from past values of research.}{$\amplitudecoefficienttwo^{\research}$}
\stoptable

\section{Equation}

\begin{equation}
\contribution^{\price}(\dummyiterator,\dummyiteratortwo) = \sum_{\dummyiteratorthree = 1}^{\dummyiteratortwo} e^{- \frac{ \dummyiterator}{e^{-\decaycoefficient_\dummyiteratorthree^\price}}}
\end{equation}
\begin{equation}
\contribution^{\research}(\dummyiterator,\dummyiteratortwo) = \sum_{\dummyiteratorthree = 1}^{\dummyiteratortwo} e^{- \frac{ \dummyiterator}{e^{-\decaycoefficient_\dummyiteratorthree^\research}}}
\end{equation}
\begin{equation}
{\bigcontribution}_{\dummyiteratortwo \price} = \amplitudecoefficient_{\dummyiteratortwo}^{\price} \frac{\sum_{\dummyiterator=0}^{\lookbacklength} \price_{\currenttime - \dummyiterator} \contribution^{\price}(\dummyiterator, \dummyiteratortwo)}{\sum_{\dummyiterator = 0}^{\lookbacklength} \contribution^{\price}(\dummyiterator, \dummyiteratortwo)} \\
\end{equation}
\begin{equation}
\bigcontribution_{\dummyiteratortwo  \research} = \amplitudecoefficient_{\dummyiteratortwo}^{\research} \frac{\sum_{\dummyiterator=0}^{\lookbacklength} \research_{\currenttime - \dummyiterator} \contribution^{\research}(\dummyiterator, \dummyiteratortwo)}{\sum_{\dummyiterator = 0}^{\lookbacklength} \contribution^{\research}(\dummyiterator, \dummyiteratortwo)} \\
\end{equation}
\begin{equation}
\position_{\currenttime} = ({\bigcontributionone}_{\price} + {\bigcontributionone}_{\research} + {\bigcontributiontwo}_{\price} + {\bigcontributiontwo}_{\research})/{\price}_{\currenttime} \\
\end{equation}
\hspace{200mm}

\noindent where $\price_\currenttime$ is the price at time $\currenttime$, $\research$ is the value of the research series, $\amplitudecoefficientone$ and $\amplitudecoefficienttwo$ are the amplitude coefficients, $\decaycoefficientone$ and $\decaycoefficienttwo$ are the decay rate coefficients and $\position$ is the resultant fractional portfolio investment.\\
Intuitively, the $\contribution$ are the exponential weightings for each historical value in the look back period, with $\bigcontribution$ the normalised sum of all the contributions, scaled by the amplitude coefficient. The total contributions are then scaled by the current price to give a dimensionless fraction of the portfolio to invest.
\hspace{200mm}
\hspace{200mm}

\keyterms
\furtherlinks
\end{document}
