\documentclass{article}
\usepackage{tocloft}
\include{common_symbols_and_format}
\renewcommand{\cfttoctitlefont}{\Large\bfseries}

\begin{document}
\logo
\rulename{Kaufman's Adaptive Moving Average} %Argument is name of rule
\tblofcontents

\ruledescription{The Kaufman's Adaptive Moving Average (KAMA), Developed by Perry Kaufman in 1998 is a moving average designed to account for market noise or volatility. The powerful trend-following indicator is based on the Exponential Moving Average (EMA) It closely follows price when noise is low and smooths out the noise when price fluctuates. A bullish crossover is indicated by the fast moving average crossing above the slow moving average. And a bearish crossover is indicated by the fast moving average crossing below the slow moving average.
}

\howtotrade
{The strategy is to identify Bullish and Bearish Crossovers. \\
Bullish Crossover:When the fast moving average cross above the slow moving average. \\
Bearish Crossover:When the fast moving average cross below the slow moving average
}

\ruleparameters %You can include however many arguments (in groups of 4) as you want!
{Slow Look Back Length}{30}{Look back length used to compute slow MA.}{$\lookbacklength_{s}$}
{Fast Look Back Length}{2}{Look back length used to compute fast MA.}{$\lookbacklength_{f}$}
{Number of periods}{10}{Number of periods used to compute $\sigma$ and $\Delta_{\currenttime}$.}{$n$}
\stoptable %must be included or Tex engine runs infinitely

\newpage
\section{Equation}
Below are the equations which govern how this specific trading rule calculates a trading position.

\begin{equation}
    \Delta_{\currenttime} = C_{\currenttime} - C_{\currenttime - n}
\end{equation}
\begin{equation}
    \sigma = \sum_{\currenttime=1}^{n} |{C_{\currenttime} - C_{\currenttime-1}}|
\end{equation}
\begin{equation}
    ER_{\currenttime} = \frac{\Delta_{\currenttime}}{\sigma}
\end{equation}
\begin{equation}
    SC_{\currenttime} = \Big[ER_{\currenttime} \times \Big(\frac{2}{\lookbacklength_{f} + 1}\Big) -
    \Big(\frac{2}{\lookbacklength_{s} + 1}\Big) + \Big(\frac{2}{\lookbacklength_{s} + 1}\Big)\Big]^2
\end{equation}
\begin{equation}
    KAMA_{\currenttime} = KAMA_{\currenttime-1} + SC_{\currenttime} \times (P_{\currenttime} - KAMA_{\currenttime-1})
\end{equation}

\\ % creates some space after equation
where:

$C_{t}$: is the close price of at time \currenttime.

$\Delta_{\currenttime}$: is the change in close price at time \currenttime.

$\sigma$: is the sum of the absolute value of last $n$ changes in close price.

$ER_{t}$: is the efficiency ratio at time \currenttime.

$SC_{\currenttime}$: is the smoothing constant at time \currenttime.

$KAMA_{\currenttime}$: is the Kaufman's Adaptive Moving Average at time \currenttime.

\keyterms
\furtherlinks %The footer
\end{document}