\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{tocloft}
\include{common_symbols_and_format}
\renewcommand{\cfttoctitlefont}{\Large\bfseries}
\begin{document}

\logo

\rulename{Moving Averages}
\tblofcontents
\ruledescription{This rule uses differentials between four moving averages to determine trade positioning. The parameters accepted are the integer length of each short average (2 parameters - one for price, one for research), the additional number of days for the longer averages (2 parameters - also, one for price, one for research) and 4 coefficients for each average's weighting contribution. The total sum is divided by the current price to calculate a position size.}

\ruleparameters
{Short price average length}{2}{Number of days in the short price
average.}{$\averagelengthshort^{\price}$}
{Long price average length}{5}{Number of additional days in the longer price average (added to the number in the short price average).}{$\averagelengthlong^{\price}$}
{Short research average length}{2}{Number of days in the short research average.}{$\averagelengthshort^{\research}$}
{Long research average length}{5}{Number of additional days in the longer research average (added to the number in the short price average).}{$\averagelengthlong^{\research}$}
{Amplitude of short price average}{1.0}{Weighting coefficient for the short term average of price.}{$\amplitudecoefficientone^{\price}$}
{Amplitude of long price average}{1.0}{Weighting coefficient for the long term average of price.}{$\amplitudecoefficienttwo^{\price}$}
{Amplitude of short research average}{1.0}{Weighting coefficient for the short term average of research.}{$\amplitudecoefficientone^{\research}$}
{Amplitude of long research average}{1.0}{Weighting coefficient for the long term average of research.}{$\amplitudecoefficienttwo^{\research}$}
\stoptable


\section{Equation}

\begin{equation}
\bigcontribution(\currenttime, \averagelength, \amplitudecoefficient, \genericfunction) = \frac{\amplitudecoefficient}{\averagelength} \sum_{\dummyiterator=0}^{\averagelength-1} \genericfunction(\currenttime - \dummyiterator)\\
\label{eq1}
\end{equation}

\begin{equation}
\position(\currenttime) = \frac{\bigcontribution(\currenttime, \averagelengthshort^{\price}, \amplitudecoefficientone^{\price}, \price)+\bigcontribution(\currenttime, (\averagelengthshort^{\price} + \averagelengthlong^{\price}), \amplitudecoefficienttwo^{\price},\price)+\bigcontribution(\currenttime, \averagelengthshort^{\research}, \amplitudecoefficientone^{\research}, \research)+\bigcontribution(\currenttime, (\averagelengthshort^{\research} + \averagelengthlong^{\research}), \amplitudecoefficienttwo^{\research}, \research)}{\price(\currenttime)} \\
\label{eq2}
\end{equation}

\hspace{200mm}

\noindent where $\position_\currenttime$ is the portfolio allocation at time $\currenttime$, $\price = \price(\currenttime)$ is the value of the price series and $\research = \research(\currenttime)$ is the value of the research series.

\hspace{200mm}
\hspace{200mm}

\keyterms

\furtherlinks

\end{document}
