\documentclass{article}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{lmodern}%
\usepackage{textcomp}%
\usepackage{lastpage}%
%
\input{common_symbols_and_format.tex}%
\usepackage{tocloft}%
\renewcommand{\cfttoctitlefont}{\Large\bfseries}%
%
\begin{document}%
\normalsize%
\logo%
\rulename{Rolling Price Level and Change Regression}%
\tblofcontents%
\ruledescription{Regresses the one-day price changes against i) the prior day's change in the price, ii) level of the price for the specified number of days.}%

\howtotrade{
    This trading rules regresses the 1-day price changes seen historical against the prior day's  change of the
     price series and level of price series: for a positive coefficient larger positions are taken if the price is increasing and/or is high in level.
}

\ruleparameters{Amplitude}{0.1}{Amplitude weighting (Kelly Fraction). 1.0 is maximum growth if regression is exact. <1.0 scales down positions taken.}{F}{Regression Length}{100}{This is the number of days used to estimate the regression coefficients.}{L}%
\stoptable%

\section{Equation}
Below are the equations which govern how this trading rule determines a trading position.
\begin{equation}
\regressionprice_\currenttime =\amplitudecoefficient_{1}\research_{\currenttime} + \amplitudecoefficient_{2}\left(\frac{\research_\currenttime}{\research_{\currenttime - 1}} - 1\right)+\constantc 
\label{eq1}
\end{equation}

The equation ($\ref{eq1}$) predicts the value of the price $\regressionprice_\currenttime$ at time $\currenttime$ using the ratio of the research value at time $\currenttime$ at $\research_\currenttime$ and the research value of the first day price changes seen historically $\research_{\currenttime-1}$.The amplitude coefficients $\amplitudecoefficient_{1}$ and  $\amplitudecoefficient_{2}$ are related to the slope of the equation fitted to the data, since in this trading rule the data behaviour is analyzed  using regression analysis. In order to calculate the resultant fractional portfolio allocation $\position_{\currenttime}$ we use the Kelly fraction to obtain the maximum results for the long run. 

\begin{equation}
\position_\currenttime = \kellyfraction \frac{\regressionprice_\currenttime}{ \rmserror_{\regressionprice}^{2}}  
\label{eq2}
\end{equation}
Additionally, the standard error $\rmserror_{\regressionprice}$ is calculated and included in equation (\ref{eq2}) to normalize the predicted price. 

\assumptions%
\keyterms%
\furtherlinks%
\end{document}
