\documentclass{article}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{lmodern}%
\usepackage{textcomp}%
\usepackage{lastpage}%
%
\input{common_symbols_and_format.tex}%
\usepackage{tocloft}%
\renewcommand{\cfttoctitlefont}{\Large\bfseries}%
%
\begin{document}%
\normalsize%
\logo%
\rulename{Rolling Price Change Regression}%
\tblofcontents%
\ruledescription{Regresses the one-day price changes against the prior day's change in the price for the specified number of days.}%

\howtotrade{
    This trading rules regresses the 1-day price changes seen historical against the prior day's change of the
     price series: larger positions are taken if the research signal is increasing.
}

\ruleparameters{Amplitude}{0.1}{Amplitude weighting (Kelly Fraction). 1.0 is maximum growth if regression is exact. <1.0 scales down positions taken.}{F}{Regression Length}{100}{This is the number of days used to estimate the regression coefficients.}{L}%
\stoptable%

\section{Equation}
Below are the equations which govern how this trading rule determines a trading position.

\begin{equation}
\regressionprice_\currenttime = \amplitudecoefficient\left(\frac{\price_\currenttime}{\price_{\currenttime - 1}} - 1\right)+\constantc 
\label{eq1}
\end{equation}

The equation ($\ref{eq1}$) predicts the value of the price $\regressionprice_\currenttime$ at time $\currenttime$ using the ratio of the market value at time $\currenttime$ at $\price_\currenttime$ and the market value of the first day price changes seen historically $\price_{\currenttime-1}$.The amplitude coefficient $\amplitudecoefficient$ is related to the slope of the equation (\ref{eq1}), since in this trading rule the data behaviour is analyzed  using regression analysis. In order to calculate the resultant fractional portfolio allocation $\position_{\currenttime}$ we use the Kelly fraction to obtain the maximum results for the long run. 

\begin{equation}
\position_\currenttime = \kellyfraction \frac{\regressionprice_\currenttime}{ \rmserror_{\regressionprice}^{2}}  
\label{eq2}
\end{equation}
Additionally, the standard error $\rmserror_{\regressionprice}$ is calculated and included in equation (\ref{eq2}) to normalize the predicted price. 

\assumptions%
\keyterms%
\furtherlinks%
\end{document}
