\documentclass{article}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{lmodern}%
\usepackage{textcomp}%
\usepackage{lastpage}%
%
\input{common_symbols_and_format.tex}%
\usepackage{tocloft}%
\renewcommand{\cfttoctitlefont}{\Large\bfseries}%
%
\begin{document}%
\normalsize%
\logo%
\rulename{Static Log Difference Regression}%
\tblofcontents
\ruledescription{Regresses the one-day price changes against the lagged  difference of research to price for the specified number of days, using coefficients estimated from the start of the data.}%

\howtotrade{Given default parameter values, if the asset drift is 0.001 and the error is 0.02 (2$\%$ daily volatility), this rule will take a $0.001 / (0.02)^2  = 2.5$ or 250$\%$ position (leveraged).}

\ruleparameters{Kelly Fraction}{0.1}{Amplitude weighting (Kelly Fraction). 1.0 is maximum growth if regression is exact. <1.0 scales down positions taken.}{$\kellyfraction$}{Regression Length}{100}{This is the number of days used to estimate the regression coefficients.}{$\lookbacklength$}%
\stoptable%

\section{Equation}
Below are the equations which govern how this trading rule determines a trading position.
\begin{equation} \label{eq1}
   \regressionprice_\currenttime =  \amplitudecoefficient  (ln(\price_{\currenttime}) - ln(\research_{\currenttime})) + \constantc,
\end{equation}

The equation ($\ref{eq1}$) predict the value of the price $\regressionprice_\currenttime$ at time $\currenttime$ using the difference from the logarithm of the price and research values. Using the logarithm function properties, we can rewrite it easily as:

\begin{equation}
       \regressionprice_\currenttime =  \amplitudecoefficient  ln\left( \frac{\price_{\currenttime}}{\research_{\currenttime}}\right)  + \constantc,
\end{equation}

Since we are using a static approach the amplitude coefficient $\amplitudecoefficient$ remains constant. In order to calculate the resultant fractional portfolio allocation $\position_{\currenttime}$ we use the Kelly fraction to obtain the maximum results for the long run. 


\begin{equation}
\position_\currenttime = \kellyfraction \frac{\regressionprice_\currenttime}{ \rmserror_{\regressionprice}^{2}}  
\label{eq2}
\end{equation}

Additionally, the standard error $\rmserror_{\regressionprice}$ is calculated and included in equation (\ref{eq2}) to normalize the predicted price. 


\assumptions%
\keyterms%
\furtherlinks%
\end{document}