\documentclass{article}
\usepackage{tocloft}
\include{common_symbols_and_format}
\renewcommand{\cfttoctitlefont}{\Large\bfseries}
\begin{document}
\logo
\rulename{True Strength Index} %Argument is name of rule
\tblofcontents

\ruledescription{The True Strength Index (TSI) is a momentum indicator used to identify overbought and oversold signals. It can also be used to indicate trend reversals using bullish and bearish crossover of the signal line and TSI line.}

\howtotrade
{The strategy is to identify the oversold and overbought markets and a momentum indicator. \\
Bullish Momentum: when the TSI line cross above signal line. \\
Bearish Momentum: when signal line cross above TSI line
}


\ruleparameters
{Window size for Exponential moving average}{25}{This is the number of time steps over which exponential contributions are sourced.}{$\lookbacklength$}
{Window size for Exponential moving average}{13}{This is the number of time steps over which exponential contributions are sourced for smoothed momentum.}{$\lookbacklength_{s}$}
{Smoothing Factor}{2}{Smoothing factor represents the weighting applied to the most recent period’s value.}{$S$}
\stoptable

\newpage
\section{Equation}
\begin{equation}
    \Delta p_{\currenttime} = p_{\currenttime} - p_{\currenttime - 1}
\end{equation}

\begin{equation}
    EMA(\Delta p_{\currenttime}, S, \lookbacklength) = \Big(\Delta p_{\currenttime} * \Big(\frac{S}{1 + \lookbacklength}\Big)\Big) + EMA_{\currenttime-1} * \Big(1-\frac{S}{1 + \lookbacklength}\Big)
\end{equation}

\begin{equation}
    EMA(|\Delta p_{\currenttime}|, S, \lookbacklength) = \Big(|\Delta p_{\currenttime}| * \Big(\frac{S}{1 + \lookbacklength}\Big)\Big) + EMA_{\currenttime-1} * \Big(1-\frac{S}{1 + \lookbacklength}\Big)
\end{equation}

\begin{equation}
    TSI = 100 \times \frac{EMA(EMA(\Delta p_{\currenttime}, S, \lookbacklength), S, \lookbacklength_{s})}{EMA(EMA(|\Delta p_{\currenttime}|, S, \lookbacklength), S,\lookbacklength_{s})}
\end{equation}
\\

where: \\

$TSI$ is True Strength Index. \\

$EMA$ is exponentially weighted moving average. \\

$p_{\currenttime}$ is current stock value. \\

$\Delta p_{\currenttime}$ is change in stock value. \\

$|\Delta p_{\currenttime}|$ is absolute change in stock value. \\

$\lookbacklength$ \ is look back length. \\

$\lookbacklength_{s}$ is look back length for smoothed momentum. \\

$S$ is the smoothing factor.

\hspace{200mm}
\hspace{200mm}
\keyterms
\furtherlinks
\end{document}